Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
font

If the {\sc precision} verification returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.
Otherwise, we found a full solution for our synthesis problem
and we are done.

>>>>

If the {\sc precision} verification returns $\mathit{false}$, then we
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
for our synthesis problem and we are done.
